---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modelplotr: Plots to evaluate the business value of predictive models

The modelplotr package makes it easy to create a number of valuable evaluation plots to assess the business value of a predictive model. Using these plots, it can be shown how implementation of the model will impact business targets like response or return on investment of a campaign. 

Plots available with modelplotr:

* cumulative gains
* cumulative lift
* response 
* cumulative response
* costs & revenues 
* profit 
* return on investment

Some benefits of using modelplotr:

* *easy to explain* plots to discuss your model with business 
* *easy to use* on top of predictive models built with caret, mlr, h2o, keras or otherwise (with or without r)
* supports both *binary and multinomial targets*
* provides *four plotting scopes*: 
  + comparing models 
  + comparing datasets 
  + comparing multiclass target classes 
  + no comparison (single line)
* *plot annotation*: highlighting specific values and adding explanatory text to guide interpretation
* *plot customization*: all textual elements, line colors
* *save plot* to file on disk

## Installation

You can install `modelplotr` from [GitHub](https://github.com/modelplot/modelplotr) with:

```{r, eval = FALSE}
devtools::install_github("modelplot/modelplotr")
```

See this blog for further details and examples of using the package.
