---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modelplotr

Plots to evaluate the business performance of predictive models in R. A number of widely used plots to assess the quality of a predictive model from a business perspective can easily be created. These plots are the cumulative gains, cumulative lift, response and cumulative response. Using these plots, it can be shown how implementation of the model will impact business targets like response on a campaign. Modelplot provides four different scopes (comparing models, comparing datasets, comparing multiclass target classes and no comparison) to support visual evaluation of predictive models.Also, these plots can be annotated by highlighting specific values and adding explanatory text to guide interpretation. See [this blog](https://modelplot.github.io) for further details and examples of using the package.

## Installation

You can install `modelplotr` from [GitHub]() with:

```{r, eval = FALSE}
devtools::install_github("modelplot/modelplotr")
```

